---
lang: en
fontsize: 10pt
format:
  cv-blocks-pdf:
    details: true
engine: knitr
# Quarto's YAML metadata merging shows the extension's own biblatexoptions
# (_extensions/cv-blocks/_extension.yml) combined with this document's --
# but only this *document-level* list actually reaches the
# `\usepackage[...]{biblatex}` line pandoc's template emits (re-confirmed
# empirically, twice). So this has to be the full list, not just an
# override, despite what the metadata merge display suggests.
# `defernumbers=true` is required for `resetnumbers=true` on
# `\newrefcontext` to take effect (silently ignored otherwise) -- this is
# what makes each `.cv-bibliography` group's `[JP1]`, `[JP2]`, ...
# numbering restart per group instead of continuing across groups.
biblatexoptions:
  - style=numeric
  - sorting=ydnt
  - defernumbers=true
  - giveninits=true
  - maxbibnames=999
  - date=year
  - doi=true
  - url=true
  - isbn=false
  - eprint=false
keywords: [Sparse models, Multi-omics integration, Reproducible research]
categories: [Statistical methods, Machine learning]
bibliography:
  - data/papers.bib
  - data/talks.bib
---

## {{< meta author >}} - Curriculum Vitae

### Researcher in Statistics

::: {.cv-header file="data/personal.yml"}
:::

### Brief summary of activities

Production
:   {{< cv_count file="data/papers.yml" group=1 >}} papers, {{< cv_count file="data/papers.yml" group=2 >}} talks.

Students
:   {{< cv_count file="data/students.yml" group=1 >}} PhD, {{< cv_count file="data/students.yml" group=2 >}} Master.

Teaching
:   Statistics in Action with R, Convex Optimization.

### Experience

::: {.cv-block file="data/experience.yml"}
:::

### Education

::: {.cv-block file="data/education.yml"}
:::

## Scientific activities

### Grants

::: {.cv-block file="data/grants.yml"}
:::

### Activities

::: {.cv-block file="data/activities.yml"}
:::

### Students

::: {.cv-block file="data/students.yml"}
:::

### Teaching

```{=latex}
Approximately 2000 hours of teaching. Lecturer at Example University from 2015 to 2024.
```

::: {.cv-block file="data/teachings.yml"}
:::

## Scientific productions

### Publications

::: {.cv-bibliography file="data/papers.yml"}
:::

## Research Projects

### DISCERN

As part of the DISCERN project, my group develops sparse graphical model estimators (see article [@doe2023example] and talk [@doe2020talk]) for integrating multi-omics data. Given a sample covariance matrix $S$, we estimate a sparse precision matrix $\hat\Theta_\lambda$ by solving

$$
\hat\Theta_\lambda = \arg\min_{\Theta \succ 0} \; -\log\det\Theta + \mathrm{tr}(S\Theta) + \lambda \|\Theta\|_1 .
$$

```{r}
#| echo: false
#| label: fig-lambda
#| fig-cap: "Estimation error as a function of the sparsity penalty"
#| fig-pos: "H"
#| fig-width: 4.2
#| fig-height: 2.2
#| message: false
suppressPackageStartupMessages(library(ggplot2))
set.seed(42)
lambda <- seq(0.05, 0.5, length.out = 6)
error <- pmax(0.9 * exp(-3 * lambda) + rnorm(6, 0, 0.02), 0.05)
df <- data.frame(lambda = lambda, error = error)

ggplot(df, aes(x = lambda, y = error)) +
  geom_line(color = "#345A8A") +
  geom_point(color = "#CC0000", size = 1.6) +
  labs(x = expression(lambda), y = "Estimation error") +
  theme_minimal(base_size = 9)
```

Increasing the penalty $\lambda$ trades estimation error for a sparser,
more interpretable graph, see @fig-lambda.

### Another project

{{< lipsum 2 >}}

See @tbl-lambda.

```{r}
#| echo: false
#| label: tbl-lambda
#| tbl-cap: "Estimation error and graph sparsity for a few penalty values"
df_tbl <- data.frame(
  Lambda = c(0.05, 0.2, 0.5),
  Error = c(0.79, 0.42, 0.19),
  Sparsity = c("12%", "48%", "81%")
)
knitr::kable(df_tbl)
```
