---
format:
  cv-blocks-pdf: default
classoption: [10pt, english]
engine: knitr
bibliography:
  - data/papers.bib
  - data/talks.bib
cv-blocks:
  lang: en
  long: true
---

{{< include _body.qmd >}}

## Research Projects

### DISCERN

As part of the DISCERN project, my group develops sparse graphical model estimators for integrating multi-omics data. Given a sample covariance matrix $S$, we estimate a sparse precision matrix $\hat\Theta_\lambda$ by solving

$$
\hat\Theta_\lambda = \arg\min_{\Theta \succ 0} \; -\log\det\Theta + \mathrm{tr}(S\Theta) + \lambda \|\Theta\|_1 .
$$

```{r}
#| echo: false
#| label: fig-lambda
#| fig-cap: "Estimation error as a function of the sparsity penalty"
#| fig-pos: "H"
#| fig-width: 4.2
#| fig-height: 2.2
#| message: false
suppressPackageStartupMessages(library(ggplot2))
set.seed(42)
lambda <- seq(0.05, 0.5, length.out = 6)
error <- pmax(0.9 * exp(-3 * lambda) + rnorm(6, 0, 0.02), 0.05)
df <- data.frame(lambda = lambda, error = error)

ggplot(df, aes(x = lambda, y = error)) +
  geom_line(color = "#345A8A") +
  geom_point(color = "#CC0000", size = 1.6) +
  labs(x = expression(lambda), y = "Estimation error") +
  theme_minimal(base_size = 9)
```

Increasing the penalty $\lambda$ trades estimation error for a sparser,
more interpretable graph, see @fig-lambda.

### Another project

{{< lipsum 2 >}}

See @tbl-lambda.

```{r}
#| echo: false
#| label: tbl-lambda
#| tbl-cap: "Estimation error and graph sparsity for a few penalty values"
df_tbl <- data.frame(
  Lambda = c(0.05, 0.2, 0.5),
  Error = c(0.79, 0.42, 0.19),
  Sparsity = c("12%", "48%", "81%")
)
knitr::kable(df_tbl)
```
